---
title: "Initial Korean covid 19"
author: "Ever De Leon"
date: "Spring 2024"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
kRdata <- kRdata %>%
mutate(across(where(is.character), as.factor))

```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 2020

$H_0$ men and women are more likely to die in South Korea than other countries through 1 Jan to 1 May         
$H_A$ men and women are not more likely to die in South Korea than other countries through 1 Jan to 1 May

### This data was retrieved from a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Your Question - Is dying independent of sex?

```{r}
plot(deceased_date~Sex,data=kRdata)
```

This graph shows the number of deceased cases in males and females. The total is very low for both but there is a slight edge in deaths towards Males.


## Graphical results - use ggplot commands to do this  

```{r}
basicNN <- ggplot(kRdata,aes(y=country,x=result))
```
 
```{r}
basicNN + geom_point()
```

This graph shows that the countries effected by the deaths of Covid19 were Mongolia and Korea.
   
## Numerical results

```{r}
cont_table <- table(kRdata$country, kRdata$result)
```

```{r}
print(cont_table)
```

With these results it shows that Korea was heavily affected by the deaths of the Covid 19 disease. To get this plot I simply made a cont_table with the different results from each country, which also revealed one death in Mongolia.


## Inferential results 



## Conclusions

